\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\author{Sho Uemura}
\title{Searching for Heavy Photons in the HPS Experiment}
\date{}
\begin{document}
\maketitle

Massive U(1) vector bosons, also known as heavy photons, are a natural consequence of many theories of physics beyond the Standard Model. Such a particle would kinetically mix with the photon, giving it an effective coupling to electric charge much smaller than the photon's direct coupling $\alpha$. The existence of such a heavy photon is a possible explanation for the cosmic ray positron excess and the muon $g-2$ anomaly. Several current and proposed experiments are dedicated to the search for a heavy photon.

The Heavy Photon Search (HPS) is a new experiment at Jefferson Lab that will search for a heavy photon with mass 20--1000 MeV and relative coupling $\alpha'/\alpha$ of $10^{-5}-10^{-10}$. 
%Heavy photons are a natural consequence of many theories of physics beyond the Standard Model, and are well motivated as a possible explanation for the cosmic ray positron excess and the muon $g-2$ anomaly. 



The HPS experiment is designed to produce heavy photons by sending the electron beam of Jefferson Lab's CEBAF accelerator through a fixed target. The heavy photons will decay to lepton pairs, possibly with some finite decay length; the HPS detector measures the momentum and decay vertex of the pairs. The invariant mass and vertex of the pairs are used to identify heavy photons using two signatures (mass resonance and displaced decay vertex).
The detector is a compact, large-acceptance forward spectrometer comprising a silicon microstrip tracker for momentum measurement and vertexing and an electromagnetic
calorimeter for triggering.


This thesis will describe the physics of and motivations for heavy photons, review the HPS experiment, and concentrate on an analysis of the HPS data to search for heavy photons decaying into $e^+e^-$ pairs.  Two analyses are planned: a simple ``bump hunt'' looking for a mass resonance, and a vertexing search taking into account both invariant mass and vertex separation.

% A key technical component of the experiment is hit time reconstruction in the tracker. The high hit rate from scattered beam electrons makes track reconstruction impossible unless we can  reject out-of-time hits by measuring hit times to a resolution of a few nanoseconds. HPS uses the APV25 readout chip to identify and reconstruct the time of multiple hits in a strip; this is a original application

This thesis will use data collected in the HPS commissioning run, scheduled for Fall 2014. A physics run in 2015 will provide additional data if necessary.

% This
% talk will cover the motivations for heavy photons and give an overview of the HPS
% experiment.


% blah blah blah

\vspace{1 cm}
\par\noindent Candidate\dotfill\null\\*
  {\raggedleft Sho Uemura\par}

\vspace{1 cm}
\par\noindent Thesis Advisor\dotfill\null\\*
  {\raggedleft John Jaros\par}
\end{document}
